Empirical Evaluation of eval in R

### 2020-08-26 inst/analysis/counts.Rmd
Add potentially useful stuff

```{r eval=TRUE}
core_data <- read_fst(params$core_datafile)
packages_data <- 
    read_fst(params$packages_datafile) %>%
    mutate(eval_source_type = "package")
kaggle_data <- 
    read_fst(params$kaggle_datafile)
    #mutate(eval_source_type == "core")

@@

all_data <-
    all_data %>%
    mutate(core_own_dependent = if_else(eval_source == "core", "core",
                                if_else(eval_source == "base", "core",
                                if_else(package == caller_package, "own",
                                        "dependent"))),
          eval_source)

core_own_dependent <-
    all_data %>%
        group_by(file, core_own_dependent) %>%
        summarize(corpus = first(corpus), eval_calls = sum(nb_ev_calls)) %>%
        ungroup() %>%
        group_by(corpus, core_own_dependent) %>%
        summarize(total_eval_calls = sum(eval_calls),
                  max_eval_calls = max(eval_calls),
                  min_eval_calls = min(eval_calls),
                  avg_eval_calls = mean(eval_calls))

>>>>

```{r eval=TRUE}
run_trace_data <- read_fst(PACKAGE_TRACE_RUNS_FILE)
parallel_kaggle_data <- read_fst(KAGGLE_LOG_FILE)

core_data <- read_fst(params$core_datafile)
packages_data <- 
    read_fst(params$packages_datafile) %>%
    mutate(eval_source_type = "package")
kaggle_data <- 
    read_fst(params$kaggle_datafile)
    #mutate(eval_source_type == "core")

@@

all_data <-
    all_data %>%
    mutate(core_own_dependent = if_else(eval_source == "core", "core",
                                if_else(eval_source == "base", "core",
                                if_else(package == eval_source, "own",
                                        "dependent"))),
          eval_source)

#all_package_programs <- 
#    run_trace_data %>%
#    filter(Exitval != 0)
#    
#
#all_kaggle_programs <-
#    parallel_kaggle_data %>% 
#    filter(Exitval == 0) %>% 
#    pull(Command) %>% 
#    map_chr(function(str) { 
#        script <- str_split(str, " ")[[1]][4]; 
#        comps <- path_split(script)[[1]]; 
#        str_c(comps[8], "/", comps[9]) 
#    })
#    
#all_files <-
#    rbind(tibble(file = run_trace_data$file, core_own_dependent = "core", corpus = "cran", nb_ev_calls = 0),
#          tibble(file = run_trace_data$file, core_own_dependent = "own", corpus = "cran", nb_ev_calls = 0),
#          tibble(file = run_trace_data$file, core_own_dependent = "dependent", corpus = "cran", nb_ev_calls = 0)) %>%
#    rbind(tibble(file = all_kaggle_programs, core_own_dependent = "core", corpus = "kaggle", nb_ev_calls = 0),
#          tibble(file = all_kaggle_programs, core_own_dependent = "own", corpus = "kaggle", nb_ev_calls = 0),
#          tibble(file = all_kaggle_programs, core_own_dependent = "dependent", corpus = "kaggle", nb_ev_calls = 0))

core_own_dependent <-
    all_data %>%
#        rbind(all_files) %>%
#        select(file, core_own_dependent, corpus, nb_ev_calls) %>%
        group_by(file, core_own_dependent) %>%
        summarize(corpus = first(corpus), eval_calls = sum(nb_ev_calls)) %>%
        ungroup() %>%
        group_by(corpus, core_own_dependent) %>%
        summarize(total_eval_calls = sum(eval_calls),
                  max_eval_calls = max(eval_calls),
                  min_eval_calls = min(eval_calls),
                  avg_eval_calls = mean(eval_calls))
